---
title: "Simulations"
author: E. Brennan Bollman
date: '`r format(Sys.time(), "%y-%m-%d")`'
output: github_document
---

```{r setup, INCLUDE = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom")) 

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d()
scale_fill_discrete = scale_fill_viridis_d()

set.seed(1)
```

## Sample simulation

Function

```{r}
sim_mean_sd = function(samp_size, mu = 3, sigma = 4) {
  
  sim_data = 
    tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
    )

  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}
```

Simulate by running this line

```{r}
sim_mean_sd(30)
```

## Let's simulate a lot

Start with a `for` loop.

```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  
  output[[i]] = sim_mean_sd(samp_size = 30)
  
}

bind_rows(output)

```

This Above doesn't have input list, just has output list.
Can use map to apply input list to a function for output list

Let's use a loop function.

```{r}
sim_results = 
  rerun(100, sim_mean_sd(samp_size = 30)) %>% 
  bind_rows()
```

Can set the `set.seed` to make sure the random sample is same each time?

Let's look at results

```{r}
sim_results %>% 
  ggplot(aes(x = mean)) + geom_density()

sim_results %>% 
  summarize(
    avg_samp_mean = mean(mean),
    sd_samp_mean = sd(mean)
  )

sim_results %>% 
  ggplot(aes(x = sd)) + geom_density()
```

## Let's try other sample sizes

Many things in statistics are dependent on sample size. Start with `for` loop to make easier.

Want to run sim code 100x for each of below n's and save results each time. Output object should match size input object so can make into tibble.

```{r}
n_list = 
  list(
    "n = 30" = 30,
    "n = 60" = 60,
    "n = 120" = 120,
    "n = 240" = 240
  )

output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = rerun(100, sim_mean_sd(samp_size = n_list[[i]])) %>% 
    bind_rows()

}

```

Put this in a simpler process

```{r}
sim_results_1 = 
  tibble(
  samp_size = c(30, 60, 120, 240)
  ) %>% 
  mutate(
    output_lists = map(.x = samp_size, ~ rerun(1000, sim_mean_sd(.x))),
    estimate_df = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_df)
```

Do some dataframe things

```{r}
sim_results_1 %>% 
  mutate(
    sample_size = str_c("n = ", samp_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  ggplot(aes(x = sample_size, y = mean)) + 
  geom_violin()
```

```{r}
sim_results_1 %>% 
  group_by(samp_size) %>% 
  summarize(
    avg_samp_mean = mean(mean),
    sd_samp_mean = sd(mean)
  )
```

Can do `cache` in {r} to set the results of sim when knit. Or can do `set.seed(1)` to get same random numbers. 
