---
title: "Iteration and listcols"
author: E. Brennan Bollman
date: '`r format(Sys.time(), "%y-%m-%d")`'
output: github_document
---

```{r setup, INCLUDE = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom")) 

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d()
scale_fill_discrete = scale_fill_viridis_d()
```

## Lists

Can put anything in list

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)

l
l$vec_numeric
l[[1]]
l[["vec_numeric"]]
mean(l[["vec_numeric"]])
```


## `for` loop

Create a new list

```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(30, mean = 0, sd = 5),
    c = rnorm(40, mean = 10, sd = 0.2),
    d = rnorm(20, mean = -3, sd = 1)
  )

list_norm
```

Pause and get my old function

```{r}
mean_and_sd = function(x) {
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

Let's use a for loop

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}

output
```

## Let's try purr::map

```{r}
output = map(list_norm, mean_and_sd)
```

what if you want a different function?

```{r}
output = map(list_norm, median)
output = map(list_norm, IQR)
```

## Variants on map

```{r}
output = map_dbl(list_norm, median)
```

```{r}
output = map_df(list_norm, mean_and_sd, .id = "input")
```

## List col

Want something that keeps track of input and output at same time.

First, create df that has listcolumn

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )
```

```{r}
listcol_df %>% 
  pull(samp)

listcol_df %>% 
  pull(name)

listcol_df %>% 
  filter(name == "a")
```

Try operations

```{r}
listcol_df$samp[[1]]

mean_and_sd(listcol_df$samp[[1]])
mean_and_sd(listcol_df$samp[[2]])
```

Can I just map to iterate the function through?

```{r}
map(listcol_df$samp, mean_and_sd)
```

listcol is in df, but still map across an element of this list

## Want to apply map function to each element of listcol and save output in my df

Can I add a list column?

```{r}
listcol_df %>% 
  mutate(
    summary = map(samp, mean_and_sd)
  )

listcol_df %>% 
  mutate(
    summary = map_df(samp, mean_and_sd)
  )

listcol_df %>% 
  mutate(
    summary = map(samp, mean_and_sd),
    medians = map_dbl(samp, median)
  )
```

## Weather Data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

